Interpolation and extrapolation-based performance measurement of Analytical and Artificial Neural Network models in predicting hot deformation behavior of a medium carbon steel

### 2023-01-26 Article.tex
Final adds to the Latex file before submission

% !TeX encoding = UTF-8
\documentclass[twoside,english,1p,final,sort&compress]{elsarticle}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\pagestyle{headings}
\usepackage{amsthm}
\usepackage{gensymb}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{accents}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{subcaption}
\usepackage{adjustbox}
\usepackage{placeins}
\usepackage{ulem}
\usepackage[colorlinks = true]{hyperref}

@@

@@

% This is used to add comments into the text
%
% Will have to be removed from final version
%
\usepackage{soul}
\usepackage{color}
\definecolor{VWyellow}{RGB}{255,251,150}
\sethlcolor{VWyellow}

\DeclareRobustCommand{\OP}[1]{\begingroup\textcolor{red}{\hl{\textbf{O.P.:} #1}}\endgroup}
\DeclareRobustCommand{\OPP}[1]{\begingroup\textcolor{red}{\hl{\textbf{O.P.:} In previous sentence #1}}\endgroup}

\begin{document}
\begin{frontmatter}

@@

\address[LGP]{Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, Tarbes, 65016, France}
\address[ETS]{École de technologie supérieure, 1100 Notre Dame St. W., Montreal, QC H3C 1K3, Canada}

\begin{abstract}
In the present work, a critical analysis of the most commonly used analytical models and of recently introduced Artificial Neural Network based models is conducted to evaluate their prediction accuracy within and outside the experimental interval used to generate them.
To this end, the high-temperature deformation behavior of a medium carbon steel was studied over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$) using hot compression tests on a Gleeble-3800 thermomechanical simulator.
The experimental flow curves were then modeled using Johnson-Cook, Modified Zerilli-Armstrong, Hansel-Spittel, Arrhenius models, the recently proposed PTM model, as well as an Artificial Neural Network model with $3$ inputs, $2$ hidden layers of $15$ and $7$ neurons, respectively, and 1 output.
The Mean Absolute Relative Error ($\MARE$) and the Root Mean Square Error ($\RMSE$) values were used to quantify the predictive accuracy of the analyzed models.
The results indicated that the Johnson-Cook and Modified Zerilli-Armstrong models presented a significant error, $\MARE$ of $21.20\%$, while the Hansel-Spittel, PTM and Arrhenius models could predict the behavior of this alloy with an error of about $3.56\%$ error.
The Artificial Neural Network model, on the other hand, showed excellent agreement, with less than a $0.62\%$ error, between the predicted and experimental flow curves.
To further validate the performance of the above models, their ability to interpolate and extrapolate the experimental data was also tested.
The Hansel-Spittel, PTM and Arrhenius analytical models showed a good interpolation and extrapolation capability, with the notable superiority of the Arrhenius model over the other two.
The Artificial Neural Networks model was, however, still the most performant among all the models.
\end{abstract}

@@

%----------------------------------------------------------------------------------
\section{Interpolation and Extrapolation Capability of Analytical and ANN Models \label{sec:IntExt}}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\section{Conclusions and future work\label{sec:Conclusion}}
%----------------------------------------------------------------------------------

@@

>>>>

% !TeX encoding = UTF-8
%% 
%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01
%%
%% 
%%
%% $Id: elsarticle-template-num.tex 190 2020-11-23 11:12:32Z rishi $
%%
%%
\documentclass[preprint,12pt,sort&compress]{elsarticle}
%\documentclass[twoside,english,1p,final,sort&compress]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\pagestyle{headings}
\usepackage{amsthm}
\usepackage{gensymb}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{accents}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{subcaption}
\usepackage{adjustbox}
\usepackage{placeins}
\usepackage{ulem}
\usepackage[colorlinks = true]{hyperref}

@@

\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

@@

% This is used to add comments into the text
%
% Will have to be removed from final version
%
%\usepackage{soul}
%\usepackage{color}
%\definecolor{VWyellow}{RGB}{255,251,150}
%\sethlcolor{VWyellow}
%
%\DeclareRobustCommand{\OP}[1]{\begingroup\textcolor{red}{\hl{\textbf{O.P.:} #1}}\endgroup}
%\DeclareRobustCommand{\OPP}[1]{\begingroup\textcolor{red}{\hl{\textbf{O.P.:} In previous sentence #1}}\endgroup}

\begin{document}

\begin{frontmatter}

@@

\affiliation[LGP]{organization={Laboratoire Génie de Production, INP/ENIT, Université de Toulouse},
             addressline={47 Av d'Azereix},
             city={Tarbes},
             postcode={65016},
             state={},
             country={France}}

\affiliation[ETS]{organization={École de technologie supérieure},
             addressline={1100 Notre Dame St. W.},
             city={Montreal},
             postcode={QC H3C 1K3},
             state={},
             country={Canada}}

\begin{abstract}
\blfootnote{This article is an open access article distributed under the terms and
conditions of the Creative Commons Attribution (CC BY) license (\href{http://creativecommons.org/licenses/by/4.0}{http://creativecommons.org/licenses/by/4.0}).} In the present work, a critical analysis of the most commonly used analytical models and of recently introduced Artificial Neural Network based models is conducted to evaluate their prediction accuracy within and outside the experimental interval used to generate them.
To this end, the high-temperature deformation behavior of a medium carbon steel was studied over a wide range of strains ($0.0-0.7$), strain rates ($0.001~\ps-5~\ps$) and temperatures ($1050\celsius-1250\celsius$) using hot compression tests on a Gleeble-3800 thermomechanical simulator.
The experimental flow curves were then modeled using Johnson-Cook, Modified Zerilli-Armstrong, Hansel-Spittel, Arrhenius models, the recently proposed PTM model, as well as an Artificial Neural Network model with $3$ inputs, $2$ hidden layers of $15$ and $7$ neurons, respectively, and 1 output.
The Mean Absolute Relative Error ($\MARE$) and the Root Mean Square Error ($\RMSE$) values were used to quantify the predictive accuracy of the analyzed models.
The results indicated that the Johnson-Cook and Modified Zerilli-Armstrong models presented a significant error, $\MARE$ of $21.20\%$, while the Hansel-Spittel, PTM and Arrhenius models could predict the behavior of this alloy with an error of about $3.56\%$ error.
The Artificial Neural Network model, on the other hand, showed excellent agreement, with less than a $0.62\%$ error, between the predicted and experimental flow curves.
To further validate the performance of the above models, their ability to interpolate and extrapolate the experimental data was also tested.
The Hansel-Spittel, PTM and Arrhenius analytical models showed a good interpolation and extrapolation capability, with the notable superiority of the Arrhenius model over the other two.
The Artificial Neural Networks model was, however, still the most performant among all the models.
\end{abstract}

%%Graphical abstract
\begin{graphicalabstract}
%\includegraphics{grabs}
\end{graphicalabstract}

%%Research highlights
\begin{highlights}
\item Analytical and ANN based flow laws are identified from hot compression of medium carbon steel alloy.
\item Comparison of models is done using error measure with regard to the experiments.
\item The efficiency of each model is evaluated using interpolation and extrapolation techniques.
\item The Arrhenius model is the more accurate of all analytical models.
\item The ANN based model is the most accurate of all proposed models.
\end{highlights}

@@

%----------------------------------------------------------------------------------
\section{Interpolation and Extrapolation Capability of Models\label{sec:IntExt}}
%----------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------
\section{Conclusions\label{sec:Conclusion}}
%----------------------------------------------------------------------------------

@@

\section*{Data availability}
The raw/processed data required to reproduce these findings cannot be shared at this time due to privacy and ethical concerns.

\section*{Declaration of Competing Interest}
The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

\section*{Authors Contribution}
\textbf{Pierre Tize Mha}: Conceptualization, Data Curation, Software, Writing - Original Draft;
\textbf{Prashant Dhondapure}: Investigation, Data Curation;
\textbf{Mohammad Jahazi}: Supervision, Project administration, Funding acquisition;
\textbf{Amèvi Tongne}: Supervision;
\textbf{Olivier Pantalé}: Conceptualization, Methodology, Validation, Formal analysis, Software, Supervision, Visualization, Writing - Review \& Editing.
%Conceptualization
%Methodology
%Software
%Validation
%Formal analysis
%Investigation
%Resources
%Data Curation
%Writing - Original Draft
%Writing - Review \& Editing
%Visualization
%Supervision
%Project administration
%Funding acquisition

All authors have read and agreed to the published version of the manuscript.

\section*{Acknowledgements}
The authors acknowledge Finkl Steel-Sorel Co., École de Technologie Supérieure, and École Nationale d’ingénieurs de Tarbes, France, for providing technical data, materials, and  testing facilities.

\section*{Fundings}
This work was supported by the Natural Sciences and Engineering Research Council of Canada (NSERC) in the framework of a Collaborative Research and Development project (CRD) [Grant number 5364418].
